### 2019-04-25 Chapters/Chap3/ModelsNNN.tex
more spaces

\begin{align}
\label{KMH}
\hat{H}_{\text{KMH}} &= -t_1\sum_{\langle i j \rangle \sigma} \hat{c}^{\dagger}_{i\sigma}\hat{c}_{j\sigma} + i\Delta \sum_{\langle \langle i j \rangle \rangle \sigma \sigma'} \hat{c}^{\dagger}_{i\sigma} \nu_{ij} \sigma^z_{\sigma \sigma'} \hat{c}_{j\sigma'} + \text{U}\hat{D}
\end{align}

Where $\Delta$ is the intrinsic spin orbit coupling constant. $\nu_{ij}=\pm 1$ depending on whether the electron traversing from $i$ to $j$ makes a right ($+1$) or a left turn ($-1$). This Hamiltonian is described by \ref{BigHam} if we set $\bs{\Delta}_{1,ij} = 0$, $t_2 = 0$ and $\bs{\Delta}_{2,ij} = -i\Delta \nu_{ij} \hat{e}_z$. Then, the effective spin model will be:

\begin{equation}
\label{KMHeff}
\hat{H}_{\text{KMH}}^{\text{eff}}(t) = \sum_{\langle i,j \rangle} J_{ij} \bs{S}_i \cdot\bs{S}_j + \sum_{\langle \langle i,j \rangle \rangle} \bs{S}_i \bs{\Gamma}_{ij} \bs{S}_j 
\end{equation}

With and:

\begin{align*}
J_{ij} &= t_1^2\mathcal{M}(\alpha_{ij}, \text{U}, \omega, t) \\
\bs{\Gamma}_{ij} &= \Delta^2 \text{diag}(-1,-1,1)\mathcal{M}(\alpha_{ij}, \text{U}, \omega, t)
\end{align*}

according to \ref{JGeneral} and \ref{GammaGeneral}. Notice that:

\begin{equation*}
\bs{S}_i \bs{\Gamma}_{ij} \bs{S}_j = \Delta^2 \mathcal{M}(\alpha_{ij}, \text{U}, \omega, t) \left(S_i^zS_j^z - S_i^xS_j^x - S_i^yS_j^y\right)
\end{equation*}

This describes a type of anisotropic exchange interaction known as XXZ Heisenberg model for next nearest neighbors. Notice that the anisotropic term breaks the SU(2) symmetry of the bare Heisenberg model. The same spin model is obtained in \cite{Rachel2010} without the laser perturbation, this model has a much richer phase diagram than the $J_1-J_2$ Heisenberg model \cite{Vaezi2012}. If the laser field is not too strong so that we can assume $\mathcal{M}(\alpha_{ij}, \text{U}, \omega, t) > 0$, then $\Gamma^{zz}_{ij} > 0$. Therefore we see that this interaction favors antiferromagnetic order in the $\hat{e}_z$ direction and ferromagnetic order in the $\hat{e}_x-\hat{e}_y$ plane. The exchange interaction $J_{ij}$ will favor antiferromagnetic order for nearest neighbors, so that next nearest neighbors will tend to be aligned. Therefore, $\Gamma^{zz}_{ij}$ will compete against $J_{ij}$ in the $\hat{e}_z$ direction. In the $\hat{e}_x-\hat{e}_y$ plane, $\bs{\Gamma}_{ij}$ will favor ferromagnetic order between next nearest neighbors, which adds to the effect of $J_{ij}$. In general the strength of the exchange interaction will be larger and the net effect of $\bs{\Gamma}_{ij}$ will be a tilting of the spins towards the $\hat{e}_x$-$\hat{e}_y$ plane.

@@

\begin{equation}
\label{MKMH}
\hat{H} = - t_1\sum_{\langle i,j \rangle, \sigma} \hat{c}_{i \sigma}^\dagger \hat{c}_{j \sigma} -
	\sum_{\langle \langle i,j \rangle \rangle, \sigma}(t_2 - i\Delta\nu_{ij}\sigma^z_{\sigma, \sigma})\hat{c}_{i \sigma}^\dagger \hat{c}_{j \sigma} + 
	\text{U}\hat{D}
\end{equation}

\begin{figure}
\centering
\includegraphics[width=0.5\columnwidth]{../Figures/kmh.png}
\caption{A honycomb cell with NN hopping $t_1$, NNN hopping $t_2$ and intrinsic SOI $\Delta$. $\nu_{ij} = \pm 1$ depending on whether the electron traversing from $i$ to $j$ makes a right ($+1$) or a left turn ($-1$).}
\label{fig:MKMH}
\vspace*{-6pt}
\end{figure}

@@

\begin{equation}
\label{MKMHeff}
\hat{H}_{\text{eff}}(t) = \sum_{\langle i,j \rangle} J_{1,ij}\bs{S}_i\cdot\bs{S}_j + \sum_{\langle \langle i,j \rangle \rangle} \left\{ J_{2,ij}\bs{S}_i\cdot\bs{S}_j + \bs{D}_{2,ij}\cdot \bs{S}_i \times \bs{S}_j + \bs{S}_i \bs{\Gamma}_{ij} \bs{S}_j \right\}
\end{equation}

\begin{align*}
J_{1,ij} &= t_1^2\mathcal{M}(\alpha_{ij}, \text{U}, \omega, t) \\
J_{2,ij} &= t_2^2\mathcal{M}(\alpha_{ij}, \text{U}, \omega, t) \\
\bs{D}_{2,ij} &= 2\nu_{ij} t_2 \Delta \hat{e}_z \mathcal{M}(\alpha_{ij}, \text{U}, \omega, t) \\
\bs{\Gamma}_{2,ij} &= \Delta^2 \text{diag}(-1,-1,1) \mathcal{M}(\alpha_{ij}, \text{U}, \omega, t) 
\end{align*}

Such a Hamiltonian was first proposed by S. A. Owerre to model honeycome topological magnon insulators \cite{Owerre2016} \cite{Elyasi2018}. Experimental results regarding topological properties of spin waves in honeycomb ferromagnet Cr$I_3$ can only be understood by considering this Hamiltonian \cite{Chen2018}. This model is also relevant for the study of Spin Hall effects of Weyl magnons \cite{Zyuzin2018} \cite{Sekine2016}.

@@

\begin{align}
\hat{H}_{\text{eff}}(t) = &\sum_{\langle i,j \rangle ^*} \left\{ J_{1,ij}\bs{S}_i\cdot\bs{S}_j + \bs{D}_{1,ij}\cdot \bs{S}_i \times \bs{S}_j + \bs{S}_i\bs{\Gamma}_{1,ij}\bs{S}_j\right\} + \nonumber \\
&\sum_{\langle \langle i,j \rangle \rangle^*} \left\{ J_{2,ij}\bs{S}_i\cdot\bs{S}_j + \bs{D}_{2,ij} \cdot\bs{S}_i \times \bs{S}_j + \bs{S}_i\bs{\Gamma}_{2,ij}\bs{S}_j\right\}
\end{align}

$\langle i,j \rangle ^*$ denotes sum over NN avoiding repeating the same two sites. The coupling factors are:

\begin{align}
J_{n,ij} &= 4\frac{t_n^2}{U^*_{ij}} \\
\bs{D}_{n,ij} &= 8\frac{t_n i\bs{\Delta}_{n,ij}}{U^*_{ij}} \\
\Gamma_{n,ij}^{\alpha \beta} &= \frac{4}{U^*_{ij}}(\delta_{\alpha \beta} \bs{\Delta}_{n,ij}^2 - 2\Delta_{n,ij}^\alpha\Delta_{n,ij}^\beta )
\end{align}

\begin{equation}
\frac{1}{U^*_{ij}} =  \frac{1}{2}\left( \frac{1}{\text{U} - e\bs{\vec{R}}_{ij}\cdot\bs{\vec{E}}_0} + \frac{1}{\text{U} + e\bs{\vec{R}}_{ij}\cdot\bs{\vec{E}}_0} \right)
\end{equation}

>>>>

\begin{align}
\label{KMH}
\hat{H}_{\text{KMH}} &= -t_1\sum_{\langle i j \rangle \sigma} \hat{c}^{\dagger}_{i\sigma}\hat{c}_{j\sigma} + i\Delta \sum_{\langle \langle i j \rangle \rangle \sigma \sigma'} \hat{c}^{\dagger}_{i\sigma} \nu_{ij} \sigma^z_{\sigma \sigma'} \hat{c}_{j\sigma'} + \text{U}\hat{D}
\end{align}
Where $\Delta$ is the intrinsic spin orbit coupling constant. $\nu_{ij}=\pm 1$ depending on whether the electron traversing from $i$ to $j$ makes a right ($+1$) or a left turn ($-1$). This Hamiltonian is described by \ref{BigHam} if we set $\bs{\Delta}_{1,ij} = 0$, $t_2 = 0$ and $\bs{\Delta}_{2,ij} = -i\Delta \nu_{ij} \hat{e}_z$. Then, the effective spin model will be:

\begin{equation}
\label{KMHeff}
\hat{H}_{\text{KMH}}^{\text{eff}}(t) = \sum_{\langle i,j \rangle} J_{ij} \bs{S}_i \cdot\bs{S}_j + \sum_{\langle \langle i,j \rangle \rangle} \bs{S}_i \bs{\Gamma}_{ij} \bs{S}_j 
\end{equation}
With and:

\begin{align*}
J_{ij} &= t_1^2\mathcal{M}(\alpha_{ij}, \text{U}, \omega, t) \\
\bs{\Gamma}_{ij} &= \Delta^2 \text{diag}(-1,-1,1)\mathcal{M}(\alpha_{ij}, \text{U}, \omega, t)
\end{align*}
according to \ref{JGeneral} and \ref{GammaGeneral}. Notice that:

\begin{equation*}
\bs{S}_i \bs{\Gamma}_{ij} \bs{S}_j = \Delta^2 \mathcal{M}(\alpha_{ij}, \text{U}, \omega, t) \left(S_i^zS_j^z - S_i^xS_j^x - S_i^yS_j^y\right)
\end{equation*}
This describes a type of anisotropic exchange interaction known as XXZ Heisenberg model for next nearest neighbors. Notice that the anisotropic term breaks the SU(2) symmetry of the bare Heisenberg model. The same spin model is obtained in \cite{Rachel2010} without the laser perturbation, this model has a much richer phase diagram than the $J_1-J_2$ Heisenberg model \cite{Vaezi2012}. If the laser field is not too strong so that we can assume $\mathcal{M}(\alpha_{ij}, \text{U}, \omega, t) > 0$, then $\Gamma^{zz}_{ij} > 0$. Therefore we see that this interaction favors antiferromagnetic order in the $\hat{e}_z$ direction and ferromagnetic order in the $\hat{e}_x-\hat{e}_y$ plane. The exchange interaction $J_{ij}$ will favor antiferromagnetic order for nearest neighbors, so that next nearest neighbors will tend to be aligned. Therefore, $\Gamma^{zz}_{ij}$ will compete against $J_{ij}$ in the $\hat{e}_z$ direction. In the $\hat{e}_x-\hat{e}_y$ plane, $\bs{\Gamma}_{ij}$ will favor ferromagnetic order between next nearest neighbors, which adds to the effect of $J_{ij}$. In general the strength of the exchange interaction will be larger and the net effect of $\bs{\Gamma}_{ij}$ will be a tilting of the spins towards the $\hat{e}_x$-$\hat{e}_y$ plane.

@@

\begin{equation}
\label{MKMH}
\hat{H} = - t_1\sum_{\langle i,j \rangle, \sigma} \hat{c}_{i \sigma}^\dagger \hat{c}_{j \sigma} -
	\sum_{\langle \langle i,j \rangle \rangle, \sigma}(t_2 - i\Delta\nu_{ij}\sigma^z_{\sigma, \sigma})\hat{c}_{i \sigma}^\dagger \hat{c}_{j \sigma} + 
	\text{U}\hat{D}
\end{equation}
\begin{figure}
\centering
\includegraphics[width=0.5\columnwidth]{../Figures/kmh.png}
\caption{A honycomb cell with NN hopping $t_1$, NNN hopping $t_2$ and intrinsic SOI $\Delta$. $\nu_{ij} = \pm 1$ depending on whether the electron traversing from $i$ to $j$ makes a right ($+1$) or a left turn ($-1$).}
\label{fig:MKMH}
\vspace*{-6pt}
\end{figure}

@@

\begin{equation}
\label{MKMHeff}
\hat{H}_{\text{eff}}(t) = \sum_{\langle i,j \rangle} J_{1,ij}\bs{S}_i\cdot\bs{S}_j + \sum_{\langle \langle i,j \rangle \rangle} \left\{ J_{2,ij}\bs{S}_i\cdot\bs{S}_j + \bs{D}_{2,ij}\cdot \bs{S}_i \times \bs{S}_j + \bs{S}_i \bs{\Gamma}_{ij} \bs{S}_j \right\}
\end{equation}
Where:

\begin{align*}
J_{1,ij} &= t_1^2\mathcal{M}(\alpha_{ij}, \text{U}, \omega, t) \\
J_{2,ij} &= t_2^2\mathcal{M}(\alpha_{ij}, \text{U}, \omega, t) \\
\bs{D}_{2,ij} &= 2\nu_{ij} t_2 \Delta \hat{e}_z \mathcal{M}(\alpha_{ij}, \text{U}, \omega, t) \\
\bs{\Gamma}_{2,ij} &= \Delta^2 \text{diag}(-1,-1,1) \mathcal{M}(\alpha_{ij}, \text{U}, \omega, t) 
\end{align*}
Such a Hamiltonian was first proposed by S. A. Owerre to model honeycome topological magnon insulators \cite{Owerre2016} \cite{Elyasi2018}. Experimental results regarding topological properties of spin waves in honeycomb ferromagnet Cr$I_3$ can only be understood by considering this Hamiltonian \cite{Chen2018}. This model is also relevant for the study of Spin Hall effects of Weyl magnons \cite{Zyuzin2018} \cite{Sekine2016}.

@@

\begin{align}
\hat{H}_{\text{eff}}(t) = &\sum_{\langle i,j \rangle ^*} \left\{ J_{1,ij}\bs{S}_i\cdot\bs{S}_j + \bs{D}_{1,ij}\cdot \bs{S}_i \times \bs{S}_j + \bs{S}_i\bs{\Gamma}_{1,ij}\bs{S}_j\right\} + \nonumber \\
&\sum_{\langle \langle i,j \rangle \rangle^*} \left\{ J_{2,ij}\bs{S}_i\cdot\bs{S}_j + \bs{D}_{2,ij} \cdot\bs{S}_i \times \bs{S}_j + \bs{S}_i\bs{\Gamma}_{2,ij}\bs{S}_j\right\}
\end{align}
$\langle i,j \rangle ^*$ denotes sum over NN avoiding repeating the same two sites. The coupling factors are:

\begin{align}
J_{n,ij} &= 4\frac{t_n^2}{\text{U}^*_{ij}} \\
\bs{D}_{n,ij} &= 8\frac{t_n i\bs{\Delta}_{n,ij}}{\text{U}^*_{ij}} \\
\Gamma_{n,ij}^{\alpha \beta} &= \frac{4}{\text{U}^*_{ij}}(\delta_{\alpha \beta} \bs{\Delta}_{n,ij}^2 - 2\Delta_{n,ij}^\alpha\Delta_{n,ij}^\beta )
\end{align}
Where:

\begin{equation}
\frac{1}{\text{U}^*_{ij}} =  \frac{1}{2}\left( \frac{1}{\text{U} - e\bs{\vec{R}}_{ij}\cdot\bs{\vec{E}}_0} + \frac{1}{\text{U} + e\bs{\vec{R}}_{ij}\cdot\bs{\vec{E}}_0} \right)
\end{equation}
We thus see that, again, the effect of a static electric field can be taken into consideration by a renormalization of the onsite interaction $\text{U}_{ij}^*$.
\end{subsection}

### 2019-04-25 Chapters/Chap3/Numerics.tex
Figure2 changes
cdots and spaces
more spaces

@@

\begin{equation}
\frac{E(\theta)}{2S^2} = -|J_1|\cos(\theta) - |D_2|\sin(2 \theta)
\end{equation}

and the energy is minimized for $\theta^* = \arcsin(\frac{-\frac{J_1}{D_2} + \sqrt{(\frac{J_1}{D_2})^2+32}}{8})$, i.e. $\theta^* = \theta^*(\frac{J_1}{D_2})$. This is the correct minimization for $J_1, D_2 > 0$. Next we will show numerically that the ratio between the NN and NNN parameters, $\frac{J_1}{D_2}$, can be modulated by the intensity of the field, and therefore the field can be used to control the SDW wavevector.

@@

\begin{align}
J_{1,ij} &= J_{1,ij}^0  \sum_{n} \frac{\mathcal{J}_n(\alpha_{ij})^2}{1+n\frac{\omega}{\text{U}}} \\
D_{2,ij} &= D_{2,ij}^0  \sum_{n} \frac{\mathcal{J}_n(\alpha_{ij})^2}{1+n\frac{\omega}{\text{U}}}
\end{align}

Where $\bs{D}_{2,ij} = \hat{e}_z D_{2,ij}$ and where $J_{1,ij}^0 = J_{1}^0 = \frac{2t_1^2}{\text{U}}$ and $D_{2,ij}^0 = -\frac{4t_2\Delta\nu_{ij}}{\text{U}}$. Since $\mathcal{J}_n(-x) = (-1)^n\mathcal{J}_n(x)$ the dependance is on $|\alpha_{ij}|$ only. Now, using \ref{Def_alpha}, for circularly polarized light we have $|\alpha_{ij}| = \frac{1}{\sqrt{2}}e|\vec{R}_{ij}| \frac{E_0}{\omega} = \frac{1}{\sqrt{2}}ea \frac{E_0}{\omega} \frac{|\vec{R}_{ij}|}{a} = \frac{|\vec{R}_{ij}|}{\sqrt{2}a} \mathcal{E}$, where $a$ is the lattice constant and $\mathcal{E} = \frac{eaE_0}{\omega}$. Now, for $J_{1,ij}$, $i$ and $j$ are NN and so we can write $|\vec{R}_{ij}|=a$, whereas for $D_{2,ij}$, $i$ and $j$ are NNN and so $|\vec{R}_{ij}|=2a$. Thus:

\begin{align}
J_{1,ij} &= J_{1} = J_{1}^0  \sum_{n} \frac{\mathcal{J}_n(\frac{1}{\sqrt{2}}\mathcal{E})^2}{1+n\frac{\omega}{\text{U}}} \\
D_{2,ij} &= D_{2,ij}^0  \sum_{n} \frac{\mathcal{J}_n(\sqrt{2}\mathcal{E})^2}{1+n\frac{\omega}{\text{U}}}
\end{align}

In each case the absolute vale is independent of $i,j$.  Now, in units $\hbar=t_1=1$ we measure energy in units of $t_1$ and frequency in units of $\frac{t_1}{\hbar}$. Then, for $t_2 = 0.1$, $\Delta = 0.5$, $\text{U} = 10$ and $\omega = 4, 14$ we obtain the plots in Figure \ref{Fig3.1:NNvsNNN}. The ratio $\frac{J_{1,ij}}{D_{2,ij}}$ is plotted in Figure \ref{Fig3.1:ratio}. The field can change the sign of $J_1$ and $D_2$ for strong amplitudes. Finally, in Figure \ref{Fig3.2} we plot the SDW NN angle $\theta$ limited to the case $J_1 > 0$ and $D_2 > 0$.

\begin{figure}
\centering
\begin{subfigure}{.45\textwidth}
  %\centering
  \includegraphics[width=1\linewidth]{Figures/NNvsNNN.pdf}
  \caption{$\frac{J_{1}}{J_{1}^0}$ and $\frac{D_{2,ij}}{D_{2,ij}^0}$ are plotted as function of $\mathcal{E}$. Similar results are obtained in \cite{Mentink2015} for $J_{1}$. Solid lines are for $\omega = 4$ and dashed lines are for $\omega = 14$.}
  \label{Fig3.1:NNvsNNN}
\end{subfigure}%
\hspace*{\fill}
\begin{subfigure}{.45\textwidth}
  %\centering
  \includegraphics[width=1\linewidth]{Figures/ratio.pdf}
  \caption{$\frac{J_{1}}{D_{2,ij}}$ is plotted as function of $\mathcal{E}$, it diverges every time $D_{2,ij}$ changes sign. Solid lines are for $\omega = 4$ and dashed lines are for $\omega = 14$.}
  \label{Fig3.1:ratio}
\end{subfigure}
\label{Fig3.1}
\end{figure}

@@

\begin{align}
\bs{S}_1(\bs{r}) &= S\left( \cos(\bs{Q}\bs{r}), \sin(\bs{Q}\bs{r}), 0 \right) \\
\bs{S}_2(\bs{r}) &= -S\left( \cos(\bs{Q}\bs{r} + \theta), \sin(\bs{Q}\bs{r} + \theta), 0 \right)
\end{align}

The $1, 2$ subindex stands for the sublattice. The $\hat{e}_z$ component vanishes in order to minimize the contribution of the pseudodipolar interaction. Let $Q_a = \bs{Q}\hat{\bs{a}}$ and $Q_b = \bs{Q}\hat{\bs{b}}$, where $\hat{\bs{a}}$ and $\hat{\bs{b}}$ are the primitive cell vectors. Then, the classical energy per spin is given by:

\begin{align}
\frac{E}{NS^2} &= -\frac{J_1}{2}\left( \cos(\theta) + \cos(\theta - Q_a - Q_b) + \cos(\theta - Q_b) \right) + \nonumber \\
&+ (J_2-\Gamma) \left( \cos(Q_a) + \cos(Q_b) + \cos(Q_a+Q_b) \right)+ \nonumber \\
&+D_2\left( \sin(Q_a) + \sin(Q_b) + \sin(Q_a+Q_b) \right)
\end{align}

Notice that when the spins are constrained in the $\hat{e}_x, \hat{e}_y$ plane, the anisotropic interaction $\bs{S}_i\bs{\Gamma}_{ij}\bs{S}_j$ becomes a ferromagnetic interaction. The minimization of this energy will lead to an involved phase diagram in the $J_1, J_2, D_2, \Gamma_2$ space (or equivalently, in the $t_1, t_2, \Delta$ space). We will not attempt to describe this phase diagram. However, as we have shown in the one dimensional case, by modulating the laser amplitude we can control the ratio between the NN and NNN coupling factors, and thus the parameters $\bs{Q}$ and $\theta$ of the system state.

>>>>

In this section we will make a short numerical study of the analytic results obtained in the previous sections. Additionally, for the one dimensional spin chain we will show the tilting angle between spins in presence of DMI, $\theta$ can be controlled with the laser field.

@@

\begin{equation}
\frac{E(\theta)}{2S^2} = -|J_1|\cos(\theta) - |D_2|\sin(2 \theta)
\end{equation}
and the energy is minimized for $\theta^* = \arcsin(\frac{-\frac{J_1}{D_2} + \sqrt{(\frac{J_1}{D_2})^2+32}}{8})$, i.e. $\theta^* = \theta^*(\frac{J_1}{D_2})$. This is the correct minimization for $J_1, D_2 > 0$. Next we will show numerically that the ratio between the NN and NNN parameters, $\frac{J_1}{D_2}$, can be modulated by the intensity of the field, and therefore the field can be used to control the SDW wavevector.

@@

\begin{align}
J_{1,ij} &= J_{1,ij}^0  \sum_{n} \frac{\mathcal{J}_n(\alpha_{ij})^2}{1+n\frac{\omega}{\text{U}}} \\
D_{2,ij} &= D_{2,ij}^0  \sum_{n} \frac{\mathcal{J}_n(\alpha_{ij})^2}{1+n\frac{\omega}{\text{U}}}
\end{align}
Where $\bs{D}_{2,ij} = \hat{e}_z D_{2,ij}$ and where $J_{1,ij}^0 = J_{1}^0 = \frac{2t_1^2}{\text{U}}$ and $D_{2,ij}^0 = -\frac{4t_2\Delta\nu_{ij}}{\text{U}}$. Since $\mathcal{J}_n(-x) = (-1)^n\mathcal{J}_n(x)$ the dependance is on $|\alpha_{ij}|$ only. Now, using \ref{Def_alpha}, for circularly polarized light we have $|\alpha_{ij}| = \frac{1}{\sqrt{2}}e|\vec{R}_{ij}| \frac{E_0}{\omega} = \frac{1}{\sqrt{2}}ea \frac{E_0}{\omega} \frac{|\vec{R}_{ij}|}{a} = \frac{|\vec{R}_{ij}|}{\sqrt{2}a} \mathcal{E}$, where $a$ is the lattice constant and $\mathcal{E} = \frac{eaE_0}{\omega}$. Now, for $J_{1,ij}$, $i$ and $j$ are NN and so we can write $|\vec{R}_{ij}|=a$, whereas for $D_{2,ij}$, $i$ and $j$ are NNN and so $|\vec{R}_{ij}|=2a$. Thus:

\begin{align}
J_{1,ij} &= J_{1} = J_{1}^0  \sum_{n} \frac{\mathcal{J}_n(\frac{1}{\sqrt{2}}\mathcal{E})^2}{1+n\frac{\omega}{\text{U}}} \\
D_{2,ij} &= D_{2,ij}^0  \sum_{n} \frac{\mathcal{J}_n(\sqrt{2}\mathcal{E})^2}{1+n\frac{\omega}{\text{U}}}
\end{align}
In each case the absolute vale is independent of $i,j$.  Now, in units $\hbar=t_1=1$ we measure energy in units of $t_1$ and frequency in units of $\frac{t_1}{\hbar}$. Then, for $t_2 = 0.1$, $\Delta = 0.5$, $\text{U} = 10$ and $\omega = 4, 14$ we obtain the plots in Figure \ref{Fig3.1:NNvsNNN}. The ratio $\frac{J_{1,ij}}{D_{2,ij}}$ is plotted in Figure \ref{Fig3.1:ratio}. The field can change the sign of $J_1$ and $D_2$ for strong amplitudes. Finally, in Figure \ref{Fig3.2} we plot the SDW NN angle $\theta$ limited to the case $J_1 > 0$ and $D_2 > 0$.

\begin{figure}
\centering
\begin{subfigure}{.45\textwidth}
  %\centering
  \includegraphics[width=1\linewidth]{Figures/NNvsNNN1.pdf}
  \caption{$\frac{J_{1}}{J_{1}^0}$ and $\frac{D_{2,ij}}{D_{2,ij}^0}$ are plotted as function of $\mathcal{E}$. Similar results are obtained in \cite{Mentink2015} for $J_{1}$. Solid lines are for $\omega = 4$ and dashed lines are for $\omega = 14$.}
  \label{Fig3.1:NNvsNNN}
\end{subfigure}%
\hspace*{\fill}
\begin{subfigure}{.45\textwidth}
  %\centering
  \includegraphics[width=1\linewidth]{Figures/ratio.pdf}
  \caption{$\frac{J_{1}}{D_{2,ij}}$ is plotted as function of $\mathcal{E}$, it diverges every time $D_{2,ij}$ changes sign. Solid lines are for $\omega = 4$ and dashed lines are for $\omega = 14$.}
  \label{Fig3.1:ratio}
\end{subfigure}
\label{Fig3.1}
\end{figure}

@@

\begin{align}
\bs{S}_1(\bs{r}) &= S\left( \cos(\bs{Q}\cdot\bs{r}), \sin(\bs{Q}\cdot\bs{r}), 0 \right) \\
\bs{S}_2(\bs{r}) &= -S\left( \cos(\bs{Q}\cdot\bs{r} + \theta), \sin(\bs{Q}\cdot\bs{r} + \theta), 0 \right)
\end{align}
The $1, 2$ subindex stands for the sublattice. The $\hat{e}_z$ component vanishes in order to minimize the contribution of the pseudodipolar interaction. Let $Q_a = \bs{Q}\hat{\bs{a}}$ and $Q_b = \bs{Q}\hat{\bs{b}}$, where $\hat{\bs{a}}$ and $\hat{\bs{b}}$ are the primitive cell vectors. Then, the classical energy per spin is given by:

\begin{align}
\frac{E}{NS^2} &= -\frac{J_1}{2}\left( \cos(\theta) + \cos(\theta - Q_a - Q_b) + \cos(\theta - Q_b) \right) + \nonumber \\
&+ (J_2-\Gamma) \left( \cos(Q_a) + \cos(Q_b) + \cos(Q_a+Q_b) \right)+ \nonumber \\
&+D_2\left( \sin(Q_a) + \sin(Q_b) + \sin(Q_a+Q_b) \right)
\end{align}
Notice that when the spins are constrained in the $\hat{e}_x, \hat{e}_y$ plane, the anisotropic interaction $\bs{S}_i\bs{\Gamma}_{ij}\bs{S}_j$ becomes a ferromagnetic interaction. The minimization of this energy will lead to an involved phase diagram in the $J_1, J_2, D_2, \Gamma_2$ space (or equivalently, in the $t_1, t_2, \Delta$ space). We will not attempt to describe this phase diagram. However, as we have shown in the one dimensional case, by modulating the laser amplitude we can control the ratio between the NN and NNN coupling factors, and thus the parameters $\bs{Q}$ and $\theta$ of the system state.
